\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-27 doc/sui14/interaction.tex
interaction.tex: minor grammar, style, spelling

\changes{IR signals are used for intial line-of-sight targeting; subsequently, we use bi-directions wireless communication to send IR signal status from targets to back to Glass and for device control itself. We have chosen a commercial off-the-shelf ZigBee implementation (XBee based on 802.15.4 radio) for this purpose (see Figure~\ref{fig:architecture}). This architecture was mostly chosen for reasons of expediency and we do not claim optimality for our design decisions. Future head-mounted devices could clearly integrate IR emitters; the choice of wireless technology could also change. In particular, one could substitute WiFi modules or design an all-Bluetooth network and forego intermediate layers in our design.}

@@

{\bf Scan:} The user first scans the environment to locate the position of the target. During this stage, Glass constantly sends out IR signals, and  targets offer immediate feedback when they receive a signal. The user confirms his desire to connect to a target by tapping on the Glass touchpad. Glass collects the responses from targets that have received IR reception through the backchannel of XBee. If there is only one single target in IR range, it is automatically selected. However, in a dense environment where multiple targets are within range, the user needs refine his selection.

{\bf Refine:} When disambiguation is needed, the user must make an explicit selection among the targets within his view range. We have designed multiple refinement mechanisms -- all of which enable the user to select one from a subset of targets. The user confirms a current selection with a tap. Since the purpose of this stage is to disambiguate among potential targets, we will also use {\em disambiguation} to refer to this stage. Finally, a tap confirms a decision.

>>>>

\changes{IR signals are used for initial line-of-sight targeting; subsequently, we use bi-directional wireless communication to send IR signal status from targets to back to Glass and for device control itself. We have chosen a commercial off-the-shelf ZigBee implementation (XBee based on 802.15.4 radio) for this purpose (see Figure~\ref{fig:architecture}). This architecture was mostly chosen for reasons of expediency, and could be further optimized. Future head-mounted devices could clearly integrate IR emitters; the choice of wireless technology could also change. In particular, one could substitute WiFi modules or design an all-Bluetooth network and forego the intermediate layers in our design.}

@@

{\bf Scan:} The user first scans the environment to locate the position of the target. During this stage, Glass constantly sends out IR signals, and  targets offer immediate feedback when they receive a signal. The user confirms their desire to connect to a target by tapping on the Glass touchpad. Glass collects the responses from targets that have received IR reception through the backchannel of XBee. If there is only one target in IR range, it is automatically selected. However, in a dense environment where multiple targets are within range, the user needs to refine their selection.

{\bf Refine:} When disambiguation is needed, the user must make an explicit selection among the targets within their view range. We have designed multiple refinement mechanisms -- all of which enable the user to select one from a subset of targets. The user confirms a current selection with a tap. Since the purpose of this stage is to disambiguate among potential targets, we will also use {\em disambiguation} to refer to this stage. Finally, a tap confirms a decision.
